Pre-Analysis Plan

### 2021-04-19 docs/pap/compromise-punishment-pap.Rmd
changes pap

---
title: 'Pre-Analysis Plan'
author: '16 April 2021'
output: 
  github_document:
    toc: yes
    number_sections: true
  bookdown::pdf_book:
    base_format: rticles::jss_article
editor_options: 
  chunk_output_type: console
bibliography: references.bib
---

# Hypothesis

@@

First, participants complete a set of background variables on their stances on the political issues used in the experiment (i.e. corona-measures, defense, education, immigration) and on their attitude towards women in politics -- the full codeboek can be viewed [here](#).
The pre-treatment block ends with one of the two attention checks included in this survey.
When participants fail this attention check, a warning appears asking them to read the question again
carefully  and  to  answer  again.
Only when they have answered it correctly, they enter the first round of the experiment.
After each round of the experiment, some filler questions are asked about the respondents demographics.
The stimuli in the experiment are news messages in the same style as the Dutch news website [nu.nl](https://www.nu.nl/).
In these news messages, we manipulate: a) the _gender_ of the politician (male vs. female); b) the _migration background_ of the politician (based on a Arabic sounding name (Rachid(a) Amezian) or a native Dutch sounding name (Karel/Karin van der Kleijn)); and c) whether the politician _striked a compromise or not_.
This creates a full `2*2*2` factorial experiment with four rounds.
Every round, the news message covers a new issue.
The issues are: "defense" (increase cooperation of the defense units), "immigration" (immigration stop in western countries), "education" (expansion creative elementary school activities), "COVID-19" (emergency legislation to combat COVID-19).
For every round, the politicians name, and thereby gender and immigration background, are manipulated in the text and in the picture as well as the decision to strike a compromise.
For an illustration of the stimulus material, see the Figure below.
All manipulated elements are within the blue boxes.

```{r ssa-logo, fig.align = 'center', out.width = "75%", fig.cap = "The new SSA logo, which is actually a scatterplot, which is super neat!", echo = FALSE}
knitr::include_graphics(here::here("docs/pap/FMPdefensie_annotated.png"))
```

@@

## Power Analysis
As detailed in [Section 4](#analysis), I conduct an OLS regression within a multiverse approach [@simonsohn2019specification,@steegen2016increasing] using the four post-treatment questions on the politician's a) leadership evaluaton (scale); b) general favorability; c) representative quality; and d) career perspective as dependent variable and the three manipulations (gender, migration background and whether or not the politician is willing to strike a compromise ) as independent variables.
Each hypothesis is tested separately for all four issues.

>>>>

---
title: 'Pre-Analysis Plan'
author: '16 April 2021'
output: 
  pdf_document:
    toc: yes
    number_sections: true
editor_options: 
  chunk_output_type: console
bibliography: references.bib
header-includes:
   - \usepackage{floatrow}
   - \floatsetup[figure]{capposition=top}
---

\newpage
# Hypothesis

@@

First, participants complete a set of background variables on their stances on the political issues used in the experiment (i.e. corona-measures, defense, education, immigration) and on their attitude towards women in politics -- the full codeboek can be viewed [here](#).
The pre-treatment block ends with one of the two attention checks included in this survey.
When participants fail this attention check, a warning appears asking them to read the question again
carefully  and  to  answer  again.
Only when they have answered it correctly, they enter the first round of the experiment.
After each round of the experiment, some filler questions are asked about the respondents demographics.
The stimuli in the experiment are news messages in the same style as the Dutch news website [nu.nl](https://www.nu.nl/).
In these news messages, we manipulate: a) the _gender_ of the politician (male vs. female); b) the _migration background_ of the politician (based on a Arabic sounding name (Rachid(a) Amezian) or a native Dutch sounding name (Karel/Karin van der Kleijn)); and c) whether the politician _striked a compromise or not_.
This creates a full `2*2*2` factorial experiment with four rounds.
Every round, the news message covers a new issue.
The issues are: "defense" (increase cooperation of the defense units), "immigration" (immigration stop in western countries), "education" (expansion creative elementary school activities), "COVID-19" (emergency legislation to combat COVID-19).
For every round, the politicians name, and thereby gender and immigration background, are manipulated in the text and in the picture as well as the decision to strike a compromise.
For an illustration of the stimulus material, see Figure \ref{fig:treatment_example}.
All manipulated elements are within the blue boxes.

```{r ssa-logo, fig.align = 'center', out.width = "100%", fig.cap = "\\label{fig:treatment_example}Annotated Example of Stimulus Material", echo = FALSE, fig.topcaption=TRUE}
knitr::include_graphics(here::here("docs/pap/FMPdefensie_annotated.png"))
```

@@

## Power Analysis
As detailed in [Section 4](#analysis), I conduct an OLS regression within a multiverse approach [@simonsohn2019specification;@steegen2016increasing] using the four post-treatment questions on the politician's a) leadership evaluaton (scale); b) general favorability; c) representative quality; and d) career perspective as dependent variable and the three manipulations (gender, migration background and whether or not the politician is willing to strike a compromise ) as independent variables.
Each hypothesis is tested separately for all four issues.
